CFF GCT Study

### 2025-06-10 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
additional plots for Larry (again)
updated GCT figures

  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min")

@@

@@

@@

@@

# GCTpl, RCG, and HbA1c

@@

  pivot_longer(c(`GCT 60 min plasma`, `GCT 0 min capillary`, HbA1c),

@@

box_p <- box_p1 + box_p2 + box_p3

@@

  pivot_longer(c(`GCT 60 min plasma`, `GCT 0 min capillary`, HbA1c),

@@

@@

@@

@@

@@

@@

@@

@@

box_p <- box_p1 + box_p2 + box_p3

@@

>>>>

  levels = c("OGTT 0 min", "OGTT 60 min", "OGTT 120 min"),
  labels = c("Fasting", "OGTT-1hG", "OGTT-2hG")

@@

  ylab("Glucose (mg/dL)") +

@@

  scale_fill_manual(values = RColorBrewer::brewer.pal(3, "Paired")) +

@@

  ylab("GCTpl (mg/dL)") +

@@

# GCTpl, RCG, HbA1c, OGTT1hr

@@

  pivot_longer(
    c(
      `GCT 60 min plasma`, `GCT 0 min capillary`, HbA1c,
      `OGTT 60 min`
    ),

@@

box_p4 <- ggplot(
  plot_df[plot_df$Measure == "OGTT 60 min", ],
  geom_hline(yintercept = 228.5, linetype = "dashed") +
  ggtitle("OGTT 60 min") +
box_p <- box_p1 + box_p2 + box_p3 + box_p4

@@

@@

  geom_hline(yintercept = 146.5, linetype = "dashed", size = 1) +

@@

  scale_colour_manual(values = RColorBrewer::brewer.pal(3, "Set2")) +

@@

    legend.position = "none", plot.title = element_text(hjust = 0.5),

@@

  geom_hline(yintercept = 98.5, linetype = "dashed", size = 1) +

@@

  geom_jitter(show.legend = F) +
  geom_hline(aes(yintercept = 5.45, linetype = "Youden Index"), size = 1) +

@@

  scale_colour_manual(values = RColorBrewer::brewer.pal(3, "Set2")) +
  scale_linetype_manual(values = c("Youden Index" = "dashed")) +

@@

    legend.title = element_blank(), plot.title = element_text(hjust = 0.5),
box_p4 <- ggplot(
  plot_df[plot_df$Measure == "OGTT 60 min", ],
  geom_hline(yintercept = 228.5, linetype = "dashed", size = 1) +
  ggtitle("OGTT 1hPG") +
  scale_colour_manual(values = RColorBrewer::brewer.pal(3, "Set2")) +
    legend.position = "none", plot.title = element_text(hjust = 0.5),

@@

box_p <- box_p1 + box_p2 + box_p4 + box_p3 + plot_layout(ncol = 4)

@@

  ylab("OGTT-1hG ") +
  xlab("GCTpl") +
